All stable state plots, with strain variation

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/3strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

---
title: All stable state plots, with strain variation
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

for(i in 1:20)
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))

@@

for(i in 1:20)
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))

@@

for(i in 1:20)
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))

@@

for(i in 1:20)
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))

>>>>

---
title: All stable state plots, with strain variation, 3 strains
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

for(i in 1:20) {
  print(paste0("Standardised level of variation = ", round(this_dat$standvar_CB_gmax[i],2)))
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
}

@@

for(i in 1:20) {
  print(paste0("Standardised level of variation = ", round(this_dat$standvar_SB_gmax[i],2)))
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
}
#fig_state_vs_o2diff(only_SB_variable[13,])
```

@@

for(i in 1:20) {
  print(paste0("Standardised level of variation = ", round(this_dat$standvar_PB_gmax[i],2)))
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
}
#fig_state_vs_o2diff(only_SB_variable[13,])
```

@@

for(i in 1:20) {
  print(paste0("Standardised level of variation = ", round(this_dat$standvar_CB_gmax[i],2)))
  print(fig_state_vs_o2diff_sidebyside_alternative(this_dat[i,]))
}
#fig_state_vs_o2diff(only_SB_variable[13,])
```

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e2 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

---
title: All stable state plots, with strain variation, 3 strains
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_3strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with strain variation, 1e2 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+02"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e3 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

---
title: All stable state plots, with strain variation, 1e2 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+02"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with strain variation, 1e3 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+03"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e5 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

---
title: All stable state plots, with strain variation, 1e3 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+03"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with strain variation, 1e5 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+05"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

### 2022-11-21 reports/stable_state_graphs/temporal/event_definition_2/9strain 1e6 wait_time/allssplots_strainvar_0.9.1.Rmd
mostly removing nonstandard stable state data

---
title: All stable state plots, with strain variation, 1e5 wait time
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+05"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

>>>>

---
title: All stable state plots, with strain variation
author: "Owen L Petchey, Uriah Daugaard, Anubhav Gupta, Rainer M. Krug, Kimberley D. Lemmen, Sofia J. van Moorsel, Marcel Suleiman, Debra Zuppinger-Dingley, Romana Limberger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    code_folding: hide
---

@@

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
